RDF Validation of Metadata \\ on Person-Level and Aggregated Data

### 2015-04-12 paper/paper7/paper7.tex
conclusion

\begin{abstract}
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e. data collected about individuals (households, businesses). 
%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
While performing research, the detailed, often access restricted person-level
data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
To ensure high quality and trust, metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.

In this paper, we show how metadata and underlying data on different level of aggregation as well as collections of these data sets are represented in RDF and how therefore used vocabularies are interrelated.
We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality and trust.

@@

Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data. 
For data archives, research institutes, and data libraries,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world (DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}}).
Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints. 
There are also specific constraint languages like \emph{Shape Expressions}\footnote{\url{http://www.w3.org/Submission/shex-primer/}}, \emph{Resource Shapes}\footnote{\url{http://www.w3.org/Submission/shapes/}} or \emph{Description Set Profiles}\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}} that more or less explicitly address the aforementioned SBE community.
Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
validation environment (\url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{the only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.

@@

The data most often used in research within the SBE community is \emph{person-level data}, i.e. data collected about individuals 
(and sometimes also businesses and households) in the form of responses to studies or taken from administrative registers
(such as hospital records, registers of births and deaths). 
The range of person-level data is very broad (covering many different domains), 
including census, education, and health data as well as all types of business, social, and labor force surveys.  
Increasingly, this type of research data is
held within data archives or data libraries after it has been collected, so that it may be
reused by future researchers. 
In performing their research, the detailed person-level
data is aggregated into less confidential multi-dimensional tables which answer particular research questions.
Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
After validating the metadata according to these constraints, portals offer added values to their customers, e.g. by searching over and comparing metadata of multiple providers.

By its nature, person-level data is highly confidential, and access is often only permitted for qualified researchers who must apply for access. 
The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregate data, in RDF \cite{Cyganiak2010}. 
Aggregate data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
The SDMX metadata standard\footnote{http://sdmx.org/} – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
allowing the RDF versions of these standards to retain that alignment.
While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
both on a different level of aggregation, 
the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
Although, in most cases aggregated data is still published in form of PDFs, 
it is more and more common to publish aggregated data as CSV files,
allowing to perform first calculations (either using all variables or only a subset).
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent aggregated and person-level data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length.

For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
as person-level data include additional variables needed for further research.
%Although not that common, the other direction is also possible, 
%i.e. researchers may use metadata on person-level data to search for aggregated data.
One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
A \emph{study} represents the process by which a data set was generated or collected.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20'). 
To determine if variables measuring \emph{age} 
- collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable, both content-driven and technology-driven validation is performed either
within our developed validation environment or by matching algorithms. 
An example for a content-driven validation is to investigate if variables are represented in a compatible way,
i.e. are the variables' code lists theoretically comparable.
Technically, it can be validated (1) if variable definitions are available, (2) if code lists are properly structured, and (3) if for each code an associated category (a human-readable label) is specified.

\tb{maybe this paragraph should be moved to one of the subsequent sections and not be part of introduction}
Data providers and harvesters do not only offer metadata but also publicly available data on different level of detail.
To ensure high data quality and trust, they have to analyze and validate the data (are fundamental data fragments available?, how does valid data look like?). 
%They validate, e.g., if fundamental data parts are available and define how valid data should look like (using syntactic rules).
Provenance (where does the data come from?) is an important aspect in evaluating data quality.
As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
data validation can only be performed semi-automatically, i.e. an automatic approach serves as basis for intellectual decisions.

This paper aims to address two main \textbf{audiences}: 
(1) metadata practitioners seeking for how to represent metadata on data sets on different aggregation levels and
(2) metadata providers and harvesters ensuring high quality metadata by validating metadata on highly complex RDF data sets.
In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and aggregated as well as person-level data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality (meta)data within this complex of data sets on different levels of aggregation (\textbf{contribution 2}, section \ref{rdf-validation}). 
The remainder of the paper is structured as follows.

@@

\textbf{Aggregated Data in RDF.}
As Eurostat provides aggregated data as CSV files, we can easily represent the two-dimensional table in RDF by means of \emph{PHDD}.
\emph{PHDD} is a vocabulary to represent aggregated and person-level data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
The two-dimensional table about \emph{formal childcare} can be downloaded as CSV file. 
The table is represented as \emph{phdd:Table} and structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
The running example table structure includes information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
The table structure relates to the table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
For the column containing the cell values in percent, e.g., the CSV column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated. 
The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
% macht mehr sinn wenn Tabelle in mehreren Dimensionen vorhanden ist ode wenn Klassifikationen wie ISCO verwendet werden

@@

Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe constraints to validate metadata on person-level, aggregated data, and thesauri.
We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
\cite{BoschZapilkoWackerowEckert2015}.

@@

\section{Implementation}

SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints.
We use \emph{SPIN}, 
a SPARQL-based way to formulate and check constraints, as basis to develop a
validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions,
%\footnote{\url{http://www.w3.org/Submission/shex-primer/}}
Resource Shapes, and the Web Ontology Language\footnote{\textcolor{red}{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/SPIN}}} \cite{BoschEckert2014-2}.
The \emph{RDF Validator} also validates RDF data to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS}.
Although accessible within our validation tool, we provide all implemented constraints\footnote{\textcolor{red}{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}} in form of SPARQL CONSTRUCT queries.
For the subsequent evaluation, we implemented 212 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets.
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
There is one SPIN construct template for each constraint type and vocabulary-specific constraint\footnote{For a comprehensive description of the \emph{RDF Validator}, we refer to \cite{BoschEckert2014-2}}.
A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.
A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in form of multiple concrete syntaxes.

\section{Evaluation}

@@

It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the metadata and data quality of real world \emph{XKOS} and \emph{PHDD} data sets.

>>>>

\begin{abstract}
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses). 
%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
While performing research, the detailed, often access restricted person-level
data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
To ensure high quality and trust, metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.

In this paper, we show how metadata and data on different level of aggregation as well as collections of these data sets are represented in RDF and how therefore used vocabularies are interrelated.
We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality and trust.

@@

Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data. 
For data archives, research institutes, and data libraries,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world (DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}}).
Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints. 
There are also specific constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the aforementioned SBE community.
Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
validation environment (\url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.

@@

The data most often used in research within the SBE community is \emph{person-level data}, i.e. data collected about individuals, businesses, and households in form of responses to studies or taken from administrative registers
(such as hospital records, registers of births and deaths). 
The range of person-level data covers many different domains and is very broad - 
including census, education, and health data as well as all types of business, social, and labor force surveys.  
Increasingly, this type of research data is
held within data archives or data libraries after it has been collected, so that it may be
reused by future researchers. 
In performing their research, the detailed person-level
data is aggregated into less confidential multi-dimensional tables which answer particular research questions.
Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
After validating the metadata according to these constraints, portals offer added values to their customers, e.g. by searching over and comparing metadata of multiple providers.

By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregate data, in RDF \cite{Cyganiak2010}. 
Aggregate data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
allowing the RDF versions of these standards to retain that alignment.
While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
both on a different level of aggregation, 
the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
Although, in most cases aggregated data is still published in form of PDFs, 
it is more and more common to publish aggregated data as CSV files,
allowing to perform first calculations (either using all variables or only a subset).
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent aggregated and person-level data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length.

For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
as person-level data include additional variables needed for further research.
%Although not that common, the other direction is also possible, 
%i.e. researchers may use metadata on person-level data to search for aggregated data.
One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
A \emph{study} represents the process by which a data set was generated or collected.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20'). 
To determine if variables measuring \emph{age} 
- collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable, both content-driven and technology-driven validation is performed.
An example for a content-driven validation is to investigate if variables are represented in a compatible way,
i.e. are the variables' code lists theoretically comparable.
Technically, it can be validated (1) if variable definitions are available, (2) if code lists are properly structured, and (3) if for each code an associated category (a human-readable label) is specified.

Data providers and harvesters do not only offer metadata but also publicly available data on different level of detail.
To ensure high data quality and trust, they have to analyze and validate the data (are fundamental data fragments available?, how does valid data look like?). 
%They validate, e.g., if fundamental data parts are available and define how valid data should look like (using syntactic rules).
Provenance (where does the data come from?) is an important aspect in evaluating data quality.
As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.

This paper aims to address two main \textbf{audiences}: 
(1) metadata practitioners seeking for how to represent metadata and data on different aggregation levels in RDF and
(2) metadata providers and harvesters ensuring high quality data and metadata by validating RDF data according to certain constraints.
In this paper, we show in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality (\textbf{contribution 2}, section \ref{rdf-validation}).

%The remainder of the paper is structured as follows.

@@

\textbf{Aggregated and Person-Level Data in RDF.}
As Eurostat provides aggregated data as CSV files, we can easily represent the two-dimensional table in RDF by means of \emph{PHDD}.
\emph{PHDD} is a vocabulary to represent aggregated and person-level data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
The two-dimensional table about \emph{formal childcare} can be downloaded as CSV file. 
The table is represented as \emph{phdd:Table} and structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
The running example table structure includes information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
The table structure relates to the table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
For the column containing the cell values in percent, e.g., the CSV column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated. 
The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
% macht mehr sinn wenn Tabelle in mehreren Dimensionen vorhanden ist ode wenn Klassifikationen wie ISCO verwendet werden

@@

Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe constraints to validate metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as constraints on data on both aggregation levels.
We assign each constraint to constraint types either corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
\cite{BoschZapilkoWackerowEckert2015}.

@@

\section{Implementation}
\label{implementation}

SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints.
We use \emph{SPIN}, 
a SPARQL-based way to formulate and check constraints, as basis to develop a
validation environment (available at \url{http://purl.org/net/rdfval-demo})\footnote{Source code downloadable at: \textcolor{red}{\url{https://github.com/boschthomas/rdf-validator}}} to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions,
%\footnote{\url{http://www.w3.org/Submission/shex-primer/}}
Resource Shapes, and the Web Ontology Language\footnote{\textcolor{red}{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/SPIN}}} \cite{BoschEckert2014-2}.
The \emph{RDF Validator} also validates RDF data to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS}.
Although accessible within our validation tool, we provide all implemented constraints\footnote{\textcolor{red}{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}} in form of SPARQL CONSTRUCT queries.
For the subsequent evaluation, we implemented 212 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets.
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
There is one SPIN construct template for each constraint type and vocabulary-specific constraint\footnote{For a comprehensive description of the \emph{RDF Validator}, we refer to \cite{BoschEckert2014-2}}.
A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.
A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in form of multiple concrete syntaxes.

\section{Evaluation}
\label{evaluation}

@@

In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}). 
We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{content-driven-validation}).
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
and propose an extensible metric to measure the continuum of severity levels.

We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS} (section \ref{implementation}).
We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the (meta)data quality of real world \emph{XKOS} and \emph{PHDD} data sets.
